sensiAnPaper1All

### 2016-01-14 sensiAnPaper1All.Rmd
adding ggplots of individual inputs

@@

>>>>

  #get the inputs here to use in ggplot investigation of model responses to inputs
  #used in a later chunk
  ggInput <- treeInput

@@

### investigating response of time-to-resistance to individual input parameters
### (while they all are varying so it may not work well)
```{r, eval=TRUE}

  #uses ggInput calculated in earlier trunk

  #first needs to transpose rows to cols
  ggInput_T <- t(ggInput)

  #function to transpose and add strategy column with the passed value
  #also add on the input columns  
  addStrategyColumn <- function(x, value, inputs){
    x <- as.data.frame( t(x) )
    x$strategy <- value
    #transpose inputs
    inputs <- as.data.frame( t(inputs) )
    #cbind onto the outputs
    x <- cbind(inputs,x)
    x
  }

  resistPointsI1_T <- addStrategyColumn(resistPointsI1,"insecticide 1",ggInput) 
  resistPointsI2_T <- addStrategyColumn(resistPointsI2,"insecticide 2",ggInput)   
  resistPointsSeq_T <- addStrategyColumn(resistPointsSeq,"Sequential",ggInput) 
  resistPointsMix1_T <- addStrategyColumn(resistPointsMix1,"Mixture 1",ggInput) 
  resistPointsMix2_T <- addStrategyColumn(resistPointsMix2,"Mixture 2",ggInput) 
  resistPointsMix3_T <- addStrategyColumn(resistPointsMix3,"Mixture 3",ggInput)

  ggInsOuts <- rbind( resistPointsI1_T, resistPointsI2_T, resistPointsSeq_T, 
                      resistPointsMix1_T, resistPointsMix2_T, resistPointsMix3_T)

  #ggplot(diamonds, aes(x=carat, y=price, color=cut)) + geom_point() + facet_wrap( ~ cut)

  #cool working!

  #this one shows no discernible pattern
  ggplot(ggInsOuts, aes(x=effectiveness_insecticide1, y=gen_cP0.5, color=strategy)) + geom_point() + facet_wrap( ~ strategy) + geom_smooth()

  #doing; for all inputs
  names_inputs <- names(ggInsOuts)[1:10]

  for(i in names_inputs)
  {
    x11()

    y <- 'gen_cP0.5'
    #color <- 'strategy'
    #coloring by exposure shows its effect even when other params are varying
    color <- 'exposure'

    print( ggplot(ggInsOuts, aes_string(x=i, y=y, color=color)) + 
             geom_point() + 
             facet_wrap( ~ strategy) + 
             geom_smooth(aes_string(x=i, y=y, color=NULL)) )
  }

  #can I facet by particular parameter ranges ?
  #or even subset the data for specific parameter ranges
